CommonMind Consortium: DLPFC

### 2020-09-21 combined_analysis/diff.networks.Rmd
Update diff networks

	# Hypothesis testing         
	df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=TRUE)

@@

# Hypothesis testing         
df_test_null = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=TRUE) 
```

@@

```{r testing}
# Hypothesis testing         
df_test.Sex = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Sex, METADATA, variable, useSLED=TRUE)
```

```{r test, eval=FALSE}
df2 = lapply( unique(df_test$Cohort), function(chrt){
	df = df_test[df_test$Cohort == chrt,]
	df$P.Value = calc_p(df$P.Value, beta_perm[[chrt]])
	df$FDR = p.adjust(df$P.Value, "fdr")
	df
})
df2 = do.call(rbind, df2)

df3 = lapply( unique(df2$Module), function(mod){

	message(mod)
	# combine p-values with Fisher's method
	p.meta = sumlog(df2$P.Value[df2$Module == mod])$p

	data.frame(Module = mod, P.Value = p.meta)
} )
df3 = do.call(rbind, df3)
df3 = df3[!is.na(df3$P.Value),]
df3$FDR = qvalue(c(1,df3$P.Value))$qvalues[-1]

df3$FDR = p.adjust(df3$P.Value, "fdr")
```

@@

```{r testing.Dx}
# Hypothesis testing     
df_test.Dx = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx, METADATA, variable, useSLED=TRUE)  
```

@@

>>>>

	# Hypothesis testing         
	df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=FALSE)

@@

# Hypothesis testing         
df_test_null = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=FALSE) 
```

```{r recalibrate.null}

df_test_recal = apply_permutation_null( df_test_null )

df_test_meta = module_meta_analsis( df_test_recal )

```

@@

```{r testing}
# Hypothesis testing         
df_test.Sex = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Sex, METADATA, variable, useSLED=FALSE)
```

@@

```{r testing.Dx}
# Hypothesis testing     
df_test.Dx = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx, METADATA, variable, useSLED=FALSE)  
```

@@

X = Rfast::matrnorm(10, 4)
Y = Rfast::matrnorm(10, 4)

C1 = cor(X)
C2 = cor(Y)
D = C1 - C2

pdf("/Users/gabrielhoffman/Dropbox/Presentations/CMC3/CMC_DE_sex/figures/diffCor.pdf")
variancePartition::plotCorrMatrix(C1, sort=FALSE, dendrogram="none")
variancePartition::plotCorrMatrix(C2, sort=FALSE, dendrogram="none")
variancePartition::plotCorrMatrix(D, sort=FALSE, dendrogram="none")
dev.off()

set.seed(1)
X1 = Rfast::matrnorm(20, 4)
X2 = Rfast::matrnorm(20, 4)
X3 = Rfast::matrnorm(20, 4)
X4 = Rfast::matrnorm(20, 4)

C1 = cor(X1)
C2 = cor(X2)
C3 = cor(X3)
C4 = cor(X4)
Da = C1 - C2
Db = C3 - C4

pdf("/Users/gabrielhoffman/Dropbox/Presentations/CMC3/CMC_DE_sex/figures/diffCor2.pdf")
variancePartition::plotCorrMatrix(C1, sort=FALSE, dendrogram="none")
variancePartition::plotCorrMatrix(C2, sort=FALSE, dendrogram="none")
variancePartition::plotCorrMatrix(C3, sort=FALSE, dendrogram="none")
variancePartition::plotCorrMatrix(C4, sort=FALSE, dendrogram="none")
variancePartition::plotCorrMatrix(Da-Db, sort=FALSE, dendrogram="none")
dev.off()
